%        File: 21AprMeeting.tex
%     Created: Tue Apr 21 10:00 AM 2015 E
% Last Change: Tue Apr 21 10:00 AM 2015 E
%
\documentclass[letterpaper,12pt]{article}

\usepackage[margin=1in]{geometry}
%\usepackage{natbib}
\usepackage{linguex}

\usepackage[]{amsmath}
\usepackage{stmaryrd}

\usepackage{forest}

\forestset{tree defaults/.style={for tree={parent anchor=south, child anchor=north},every tree node/.style={align=center,anchor=north},level/.style={sibling distance=50mm/#1},baseline}}
\usepackage{tikz}
\usepackage[backend=bibtex,style=authoryear]{biblatex}

\bibliography{GP2}
\begin{document}

\textbf{\textcite{elbourne2005situations}: Situations}
\begin{itemize}
  \item All DPs are quantificational
  \item Determiners quantify over individuals and situations and introduce situations.
  \item The quantified situations are parts of the introduced situations
\end{itemize}
\ex. $\llbracket Det \rrbracket = \lambda f \dots \lambda s.Qx.Qs^\prime:[\dots s^\prime\preceq s \dots][\dots f(x)(s^\prime)\dots]$

\begin{itemize}
  \item Compatible with a Heim/Kamp/Lewis theory of indefinites?
  \item Elbourne only seems to care about definite descriptions
\end{itemize}
\textbf{\textcite{kennedy2007vagueness}: Comparison classes}
\ex.
\a. Every member of my family is tall.
\b. $\forall y[\textbf{in-my-family}(y) \longrightarrow [\lambda x:\textbf{k}_y(x).\textbf{tall}(x)](y)\succeq \textbf{s}([\lambda x:\textbf{k}_y(x).\textbf{tall}(x)]) ]$
\z.

\begin{itemize}
  \item Each family member's height would be judged relative to a different standard depending on their age, sex, etc.
  \item $\textbf{k}_y$ restricts the domain of the adjective.
  \item \textbf{k}$_y$ is a variable over properties `related to \textit{y}'
    \begin{itemize}
      \item Kennedy calls these \textit{skolem} functions and refers the reader to \textcite{steedman2000process} for explanation.
      \item Steedman claims these skolem functions are related to but distinct from choice functions (and gives citations that I should read).
    \end{itemize}
  \item Kennedy seems to be proposing that \textbf{k}$_x$ is built into the [\textit{pos}] morpheme, and that it is usually valued contextually, but can be bound (e.g., by a quantified subject).
\end{itemize}

\end{document}


