%        File: 6June.tex
%     Created: Tue Jun 09 09:00 AM 2015 E
% Last Change: Tue Jun 09 09:00 AM 2015 E
%
% arara: pdflatex
% arara: bibtex
% arara: pdflatex
% arara: pdflatex

\documentclass[letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[backend=bibtex,style=authoryear]{biblatex}

\usepackage[]{amsmath}
\usepackage{stmaryrd}

\usepackage{linguex}

\bibliography{GP2}

\usepackage{forest}
\forestset{tree defaults/.style={for tree={parent anchor=south, child anchor=north},every tree node/.style={align=center,anchor=north},level/.style={sibling distance=50mm/#1},baseline}}

\forestset{en/.style={parent anchor=center, child anchor=center}}
\forestset{em/.style={parent anchor=north west, child anchor=north west}}

\usetikzlibrary{positioning}
\begin{document}
\begin{itemize}
  \item Discourse is binary branching.
  \item Each move introduces a partition of the domain of discourse.
\end{itemize}
\ex.
\a. A. What did the musicians wear?\\
B. The musicians wore sunglasses?
\b. 
\begin{forest}
  tree defaults
  [tell me about the musicians.
    [What did the musicians wear?
      [Sunglasses]
      [What else?]
    ]
    [What didn't the musicians wear?]
  ]
\end{forest}

\begin{itemize}
  \item This model of discourse can rule out the minimal indefinite SSs (\#\textit{a doctor is John})
\end{itemize}

\ex. $
\begin{array}[t]{lll}
  D & = & \left\{ \text{Emily, Arsalan, Paula} \right\}\\
  Lawyers & = &\left\{ \text{Emily, Arsalan} \right\}\\
  Doctors & = &\left\{ \text{Arsalan, Paula} \right\}
\end{array}
$

\ex. $\left\{x \in D | x \text{ is a doctor} \right\}^\prime =$
\a.\label{good-partition} $\left\{ x \in D | x \text{ isn't a doctor} \right\} =$\\
$\left\{ \text{Emily} \right\}$\\
\textsc{or}
\b.\label{bad-partition} $\left\{ x \in D | x \text{ is a non-doctor} \right\} =$\\
$\left\{ \text{Emily, Arsalan} \right\}$

\ex.
\a. 
\begin{forest}
  tree defaults
  [Who is a doctor?
    [$\left\{ \text{Arsalan, Paula} \right\}$]
    [Who isn't a doctor?]
  ]
\end{forest}
\b.
\begin{forest}
  tree defaults
  [Who is a doctor?
    [$\left\{ \text{Arsalan, Paula} \right\}$]
    [Who is a non-doctor?]
  ]
\end{forest}

\begin{itemize}
  \item The alternative in \ref{bad-partition} is not a proper partition.
  \item It is the only ``partition'' available for \textit{a doctor is John}  
  \item CT and Focus are associated with syntactic constituents.
    \begin{itemize}
      \item \textit{is a doctor} is a constituent.
      \item \textit{A doctor is} is not.
    \end{itemize}
\end{itemize}
\ex.
\begin{forest}
  tree defaults
  [,en
    [,en,tikz={\node [draw,fit to tree] {};},en
      [A]
      [doctor]
    ]
    [,en
      [is]
	[John,draw]
      ]
    ] 
\end{forest}

\begin{itemize}
  \item minimal indefinite SSs cannot have a CT constituent that will give us a proper partition.
\end{itemize}
\clearpage
{\Large\textbf{Outline:}}

\textbf{Background}
\begin{itemize}
  \item Specificational Clauses
    \begin{itemize}
      \item \textcite{higgins1973pseudo}
      \item \textcite{mikkelsen2004specifying}
      \item \textcite{heycock2012specification}
    \end{itemize}
  \item Discourse
    \begin{itemize}
      \item \textcite{roberts2012information}
      \item \textcite{buring2003d,buringforthcomingtopic}
    \end{itemize}
  \item Indefinites
    \begin{itemize}
      \item \textcite{diesing1992indefinites}
      \item \textcite{Heim2011definiteness}
      \item \textcite{fodorsag1982referential}
      \item others
    \end{itemize}
\end{itemize}
\textbf{The Paper}
\begin{itemize}
  \item SSs as CTs
    \begin{itemize}
      \item Exclusion of wide-scope/referential indefinites.
    \end{itemize}
  \item Discourse model
  \item \dots
\end{itemize}

\end{document}


