%        File: LitReview.tex
%     Created: Wed Aug 26 12:00 PM 2015 E
% Last Change: Wed Aug 26 12:00 PM 2015 E
%
% arara: pdflatex: {options: "-draftmode"}
% arara: biber
% arara: pdflatex: {options: "-draftmode"}
% arara: pdflatex: {options: "-file-line-error-style"}
\documentclass[GPFinal]{subfiles}

\begin{document}
Though rarely discussed in much depth, the restriction on indefinite SC subjects is often exploited for evidence in the debate over the proper syntactic/semantic analysis of SCs.
As such, I will briefly outline the analyses and how indefinite subjects fit into them.

The inversion analysis is argued for explicitly by \textcite{mikkelsen2004specifying} and \textcite{moro1997raising}, and states that that predicative copular clauses and SCs have identical underlying structures.
According to this analysis, the two sentences in \ref{ex:SCPCPair} are each derived from the same small clause structure, given in \ref{ex:CopUnderlying}, and differ in which constituent of the the small clause is raised.
Predicative clauses surface when the argument raises, and SCs surface when the predicate raises.
\ex.\label{ex:SCPCPair}
\a.\label{ex:SCPCPairPC} Ian is my favourite singer.
\b.\label{ex:SCPCPairSC} My favourite singer is Ian.

\ex.\label{ex:CopUnderlying} 
\begin{minipage}[t]{\textwidth}
  \textbf{Base Structure}\\
\begin{forest}
  tree defaults
  [,l=8mm,s=10mm
    [be] 
    [,el
      [Arg\\\textit{Ian},align=center]
      [Pred
	[\textit{my favourite singer},triangle]
      ]
    ]
  ]
\end{forest}
\end{minipage}
%$[_{VP} \text{be} [ [_{Arg} \text{Ian}] [_{Pred} \text{my favourite singer}]]]$
\a.\label{ex:PCStruct}
\begin{minipage}[t]{\textwidth}
\textbf{Predicational Clause}\\
\begin{forest}
  tree defaults
  [,l=8mm,s=10mm
    [Arg\\\textit{Ian},align=center,name=subj]
    [,el,l=8mm,s=10mm
      [be]
      [,el,l=8mm,s=5mm
	[{$\langle \text{Arg}\rangle$},name=arg]
	[Pred
	  [\textit{my favourite singer},triangle]
	]
      ]
    ]
  ]
  \draw[->,thick](arg) to[out=south west, in=south] (subj);
  \end{forest}
\end{minipage}
%$[ [_{Arg} \text{Ian} ] \ldots [_{VP} \text{be} [ t_{Arg} [_{Pred} \text{my favourite singer}]]]]$
\b.\label{ex:SCStructure}
\begin{minipage}[t]{\textwidth}
\textbf{Specificational Clause}\\
\begin{forest}
  tree defaults
  [,l=8mm,s=10mm
    [Pred
      [\textit{my favourite singer},triangle,name=subj]
    ]
    [,el,l=8mm,s=10mm
      [be]
      [,el,l=8mm,s=5mm
	[Arg\\\textit{Ian},align=center]
	[{$\langle\text{Pred}\rangle$},name=pred]
      ]
    ]
  ]
  \draw[->,thick](pred) to[out=south west, in=south] (subj);
\end{forest}
%$[ [_{Pred} \text{My favourite singer}] \ldots [_{VP} \text{be} [ [_{Arg} \text{Ian}] t_{Pred}]]]$
\end{minipage}

Semantically, this analysis requires that SC subjects be construed as predicates (type $\langle e,t\rangle$ or higher) rather than arguments (type \textit{e}).

The equational analysis, as presented by \textcite{heycockkroch1999pseudocleft}, says that both DPs in SCs are type $e$ and the copula serves to equate them.
In \ref{ex:SCPCPairSC}, then, \textit{my favourite singer} and \textit{Ian} each refers to an individual, and the copula says that they refer to the same individual.
\textcite{heycockkroch1999pseudocleft} use the restriction on indefinite subjects to argue that SC subjects cannot be construed as predicates.
If SC subjects were inverted predicates, the argument goes, we would expect all predicative phrases, including indefinite descriptions, to be acceptable.

As I will describe in more detail in section \ref{sec:Mikkelsen}, \textcite{mikkelsen2004specifying} proposes that pragmatic factors are responsible for the indefinite restriction.
Specifically, SC's have a fixed information structure, requiring their subjects to be topics, a role which indefinites are not well-suited for.
\textcite{heycock2012specification}, responds to Mikkelsen's analysis and data  by arguing that, rather than a requirement that SC subjects be topics, the indefinite restriction is actually a restriction on \textit{weak} indefinites (\textit{i.e.}, DPs headed by weak determiners) as SC subjects.

The restriction on indefinites, then is a fact that must be explained or allowed for in any syntactic/semantic analysis of SCs.

\subsection{\textcite{mikkelsen2004specifying}}\label{sec:Mikkelsen}
Line Mikkelsen's dissertation contains one of the only attempts to define the restriction on indefinite SC subjects.
Though she admits that her attempt falls short of a proper explication of the restriction, the attempt itself provides an excellent starting point for my attempt.

After arguing in favour of a predicate inversion analysis of SC, Mikkelsen considers the restriction on indefinites and concedes that, as \textcite{heycockkroch1999pseudocleft} argue, it is not predicted by the inversion analysis.
She does not concede, however, that it represents a strong argument against the inversion analysis.
The restriction on indefinites would only be strong evidence against an inversion analysis if it were a categorical restriction, which it is not.

Mikkelsen demonstrates the non-categorical nature of the restriction with the following examples
\ex.\label{ex:MikkPhilosopher} \textbf{A philosopher who seems to share the Kiparskys' intuition on some factive predicates} is Unger (1972) who argues that \dots\footnote{\textcite[][p. 195 fn8]{delacruz1976factives} cited by \textcite{mikkelsen2004specifying}}

\ex.\label{ex:MikkSpeaker} \textbf{Another speaker at the conference} was the \textit{Times} columnist Nicholas Kristof, who got Wilson's permission to mention the Niger trip in a column.\footnote{Seymore M. Hersh ``The Stovepipe'', The New Yorker, Oct 27, 2003, p. 86 cited by \textcite{mikkelsen2004specifying}}

\ex.\label{ex:MikkEmigre} \textbf{One Iraqi \'emigr\'e who has heard from the scientists' families} is Shakir al Kha Fagi, who left Iraq as a young man and runs a successful business in the Detroit area.\footnote{Seymore M. Hersh ``The Stovepipe'', The New Yorker, Oct 27, 2003, p. 86 cited by \textcite{mikkelsen2004specifying}}

\ex.\label{ex:MikkBarcan} \textbf{A doctor who might be able to help you} is Harry Barcan.\footcite{mikkelsen2004specifying}

Since the restriction is not categorical, she argues, it is not due to a semantic type mismatch, rather it must be pragmatic in nature.

Mikkelsen points out that, unlike predicational clauses, SCs have a fixed information structure.
As demonstrated in \ref{ex:MikkQandA}, SCs are infelicitous in contexts that focus the initial DP, while predicational clauses are more flexible.
\ex.\label{ex:MikkQandA}
\a. Q: Who is the winner?\\
A1: The winner is JOHN.\hfill[Specificational]\\
A2: JOHN is the winner.\hfill[Predicational]
\b. Q: What is John?\\
A1: \#The WINNER is John.\hfill[Specificational]\\
A2: John is the WINNER.\hfill[Predicational]\\
\quelle{\parencite{mikkelsen2004specifying}}
\z.

Mikkelsen argues that this fixed information structure of SCs follows from SCs being inversion structures.
Following \textcite{birner1994information,birner1996discourse}, She assumes that the discourse function of inversion is to mark the inverted material as linking a clause to previous discourse.
The inverted material, then, must be more discourse-familiar than the post-verbal logical subject.
Mikkelsen then shows that these discourse familiarity considerations can explain the acceptability of \ref{ex:MikkPhilosopher}-\ref{ex:MikkBarcan}.

This pragmatic account, while sufficient to explain the acceptability of \ref{ex:MikkPhilosopher}-\ref{ex:MikkBarcan}, does not explain why the restriction on simple indefinites as SC subjects, as shown in \ref{ex:TheData}, seems to be categorical.
That is, even if the material in a simple indefinite is familiar, the indefinite cannot be the subject of an SC.
\ex.\label{ex:MikkFamSC} Bill is a doctor. \#A doctor is John (too).

Mikkelsen suggests that the discourse familiarity requirement of inverted material clashes with the Novelty Condition on indefinites \parencite{heim1982semantics}.
She points out, however, that this cannot be the entire story, since the Novelty Condition only requires that indefinites introduce new discourse referents.
This means that, since the two instances of \textit{a doctor} in \ref{ex:MikkFamSC} do not share a discourse referent, the Novelty Condition does not rule out the indefinite subject.

Mikkelsen also suggests that those instances of familiar yet unacceptable simple indefinite SC subjects might be infelicitous because there is a general ban on repeating indefinites, as in the example below.
\ex.\label{ex:MikkRepeat} Sally is a doctor. \#A doctor came to dinner last night.

This, however, does not seem to hold.
Utterences, such as \ref{ex:MikkRepeat}, that are barred because of repeated indefinites are made better if the first occurrence of the indefinite is modified.
If the barred utterance has an SC with an indefinite subject, as in \ref{ex:MikkFamSC}, then only changing the SC will improve it.
\ex. I know many doctors.
\a. \#A doctor is Patrick.
\b. A doctor came to dinner last night.
\z.

\subsection{\textcite{heycock2012specification}}\label{sec:Heycock}
Addressing the indefinite restriction, \textcite{heycock2012specification} begins with the information structure pattern shown in \ref{ex:MikkQandA}, which she frames as a restriction on focusing SC subjects.
She notes that this is parallel to a fact about scrambling in German observed by \textcite{lenerz1977zur}.

\ex.
\ag.Wem hat Peter das Futter gegeben?\\
who.\textsc{dat} has Peter the.\textsc{acc} food given\\
``Who has Peter given the food?''
\ag. Peter hat der Katze das Futter gegeben.\\
Peter has the.\textsc{dat} cat the.\textsc{acc} food given\\
``Peter has given the cat the food''\hfill[Default order]
\bg. Peter hat das Futter der Katze gegeben.\\
Peter has the.\textsc{acc} food the.\textsc{dat} cat given\\
``Peter has given the food to the cat''\hfill[Scrambled order]
\z.
\bg. Was hat Peter der Katze gegeben?\\
what.\textsc{acc} has Peter the.\textsc{dat} cat given\\
``What has Peter given (to) the cat?''
\ag. Peter hat der Katze das Futter gegeben.\\
Peter has the.\textsc{dat} cat the.\textsc{acc} food given\\
``Peter has given the cat the food''\hfill[Default order]
\bg.\# Peter hat das Futter der Katze gegeben.\\
Peter has the.\textsc{acc} food the.\textsc{dat} cat given\\
``Peter has given the food to the cat''\hfill[Scrambled order]
\z.
\z.

As \Last demonstrates the canonical order for ditransitive objects in German is \textsc{dat} $\prec$ \textsc{acc}.
The scrambled order, \textsc{acc} $\prec$ \textsc{dat}, is unavailable when the accusative argument is focused, as shown in \Last[b-ii]. 
Just as SCs subjects cannot be focused in English, scrambled objects cannot be focused in German.

With this information structure parallel established, \textcite{heycock2012specification} attempts to extend the comparison of English SC subjects with German scrambled objects to a semantic parallel.
Following \textcite{dehoop1992case} and \textcite{diesing1992indefinites}, Heycock assumes that scrambled DPs in German are necessarily interpreted as strong DPs.
She claims that SC subjects are also restricted to strong interpretations.
As evidence for this claim she presents another parallel.
A property of weak indefinites, according to \textcite{milsark1974existential}, is that they cannot serve as subjects of Individual-Level predicates, as shown in \Next
\ex. I had been struggling with a complicated set of data \ldots
\a.?* A problem was particularly hard.
\b. One problem was particularly hard.
\b. \{?A/one\} problem that I came across was particularly hard.
\b. One of the problems was particularly hard.\hfill\parencite{heycock2012specification}

Heycock argues that the same pattern holds for indefinite SC subjects as shown in \Next.
\ex.
\a.?* A problem was that we didn't understand all the parameters.
\b. One problem was that we didn't understand all the parameters.
\b. \{A/one\} problem that I came across was that we didn't understand all the parameters.
\b. One of the problems was that we didn't understand all the parameters.\hfill\parencite{heycock2012specification}

Given these parallels, Heycock proposes that the indefinite restriction is actually a restriction on \textit{weak} indefinites as SC subjects.

This proposal is problematic for two reasons.
First, the terms \textit{weak} and \textit{strong} in this context, properly refer to interpretations rather than lexical items.
A determiner is called \textit{strong} if it is always interpreted as strong, while \textit{weak determiners} can be interpreted as either weak or strong depending on the context.
So, supposing we take \posscite{heycock2012specification} analysis to be correct, the question changes from ``Why is the indefinite X a licit SC subject, while Y is illicit?'' to ``Why can X receive a strong interpretation, while Y cannot?''.

The second, and perhaps more compelling, argument against \posscite{heycock2012specification} proposal is that it is not borne out by the data.
Although most weak quantifiers are ambiguous between weak and strong, \textit{a(n)} and \textit{sm} (the reduced form of the strong quantifer \textit{some}) do not seem to be.
Despite not being strong though, \textit{a(n)} and \textit{sm} can head SC subjects.
\ex.
\a. An UNDERrated figure in the history of generative grammar is Eric Lenneberg.
\b. Sm SIDE-effects are headache, blurred vision and sore throat.
\z.

DPs with strong quantifiers, however, do not seem to be able to function as SC subjects, as demonstrated below in \Next.
\ex.
\a. Each doctor is Mary, Bill, Sue, and John. (*Specificational)
\b.? Most early generative grammarians are Chomsky and Halle. (*Specificational)
\b.? SOME side-effects are drowsiness and blurred vision. (*Specificational)

Copular clauses with strong indefinite subjects, instead, are most naturally interpreted as identificational.
Consider also, the minimal pair in \Next, with only strong/weak varying between the two.
\ex.
\a. SOME side-effects are drowsiness and blurred vision. (*Specificational)
\b. sm side-effects are drowsiness and blurred vision.

The subject in \Last[b] is a weak indefinite because it and others like it can be used in existential constructions.
\ex. 
\a. There is \textbf{a building no-one likes} on St George Street.
\b. \textbf{a building no-one likes} is Robarts.

\ex.
\a. There are \textbf{sm side-effects}.
\b. \textbf{Sm side-effects} are headaches and dizziness. 

Contrary to \posscite{heycock2012specification} proposal, it is the weak counterpart that can be the subject of an SC.
It seems, then, that the proposal that weak indefinites are barred from being SC subjects cannot stand.

\subsection{Summary}
Each of the two approaches to explaining the indefinite restriction reviewed in this section has its own issues.
The pragmatic approach of \textcite{mikkelsen2004specifying} covers a greater portion of the data but lacks a precise and cohesive account of it.
The semantic approach of \textcite{heycockkroch1999pseudocleft} and \textcite{heycock2012specification} is more precise at the expense of its empirical coverage.
In the following sections I will outline a pragmatic explanation of the indefinite restriction that increases not only the precision of \posscite{mikkelsen2004specifying} approach, but its empirical coverage.
\end{document}
